\documentclass[12pt]{article}
\usepackage{color}
\begin{document}
\def\labelitemi{--}
\title{Schedule and Special Note}
\maketitle

\section{Schedule}


\begin{enumerate}
	\item Draw its E-R diagram.
	\begin{itemize}
		\item Almost Done
		\item {\color{blue} This will be updated as other steps progress}
	\end{itemize}
	\item Give a relational representation of the E-R diagram that allows for 2 functional preserving and lossless join decompositions. Describe its functional dependencies.
 \begin{itemize}
		\item Nov, 16th
		\item {\color{blue} We need to modify the decomposition. Im not sure how to satisfy the "allows for 2 functional preserving and lossless join decompositions" condition}
	\end{itemize}
	\item Give the two decompositions and prove that they are lossless join and functional preserving.
	\begin{itemize}
		\item Nov, 16th
	\end{itemize}
	\item Give the SQL DDLs for creating the three versions of the database.
	\begin{itemize}
		\item Nov, 21st
	\end{itemize}
	\item Fill the first database with data (at least 100 columns in each table).
	\begin{itemize}
		\item Nov, 21st
	\end{itemize}
	\item Give the SQL queries to copy the data from the first version into its 2 decompositions.
	\begin{itemize}
		\item Nov, 25th
	\end{itemize}
	\item Propose in english 3 queries that require at least 2 table joins each and such that all tables are involved in at least 2 queries.
	\begin{itemize}
		\item Nov, 25th
	\end{itemize}
	\item Propose SQL implementations of the 3 queries on all three versions of the database.
	\begin{itemize}
		\item Nov, 30th
	\end{itemize}
	\item Test the time in ns for exeuting the 3 queries on each database, by running each of them 1000 times.
	\begin{itemize}
		\item Nov, 30th
	\end{itemize}
\end{enumerate}

Due Dec, 1st, 2017. One day to check whole things and submit.

\section{Special Note}

\end{document}